# Project 1

This is the first project for CS 329E Data Visualization.
In order to reproduce this project, please follow the following instructions.

## Step 1
#### Load the correct packages
Use the following code to load the correct packages into RStudio.

```{r message = FALSE}
source("../01 Data/Profile.R", echo = TRUE)
```


## Step 2
#### Build data frames for 4 tables called __*order_details*, *orders*, *items* and *customers*__. The R code used to do this is written below.

To create the Order Details data frame:
```{r}
source("../01 Data/OrderDetailsDF.R", echo = TRUE)
```

To create the Orders data frame:
```{r}
source("../01 Data/OrdersDF.R", echo = TRUE)
```

To create the Items data frame:
```{r}
source("../01 Data/ItemsDF.R", echo = TRUE)
```

To create the Customers data frame:
```{r}
source("../01 Data/CustomersDF.R", echo = TRUE)
```

## Step 3
#### Create the plots from the data frames using **ggplot** functions.

We can now create interesting plots for each data frame we have created from the database.


For the Order Details data frame:
```{r}
source("../02 Visualizations/VisualOrderDetails.R", echo = TRUE)
```

For the Orders data frame:
```{r}
source("../02 Visualizations/VisualOrders.R", echo = TRUE)
```

For the Items data frame:
```{r}
source("../02 Visualizations/VisualItems.R", echo = TRUE)
```

For the Customers data frame:
```{r}
source("../02 Visualizations/VisualCustomers.R", echo = TRUE)
```


## Step 4
#### Use a query to produce the entire data set.

##Use the following code to merge all of the data frames together for analysis:
```{r}
source("../01 Data/EntireDF.R", echo = TRUE)
```

## Step 5
#### Produce plots using **ggplot**

Use the new data frame named *dfEntire* to recreate the following plots.
```{r}
source("../02 Visualizations/VisualDfEntire.R", echo = TRUE)
```